### 2017-04-05 paper/evaluation.tex
pass on RQ4 (part a)

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
two extreme cases: \CodeIn{JCabi} and \CodeIn{Log4J2}.  \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}

@@

\begin{itemize}
    \item \emph{\RQC}
\end{itemize}

To evaluate the support of parallel execution of test suites, we
considered the \numMedLong{} projects that ran in at least one minute
identified in Section~\ref{sec:rqA} (\ie, \medg{} and \longg{}
groups). We are interested to know if developers consider low-level
parallelism modes to amortize the execution cost (see
Section~\ref{sec:modes}). More precisely, we investigate if there are
projects with parallelization modes enabled by default or if
developers configure this feature to run only on specific scenarios
(\eg, dedicated server).  We describe our approach as follows:

\subsubsection{Test execution with parallelism enabled by default}
\label{sec:rqC-1}

We re-executed the tests from the \numMedLong{} projects and we
configured Maven to output all runtime parameters and their current
values. We run only the test bootstrap step as the actual test
execution is unnecessary to output the runtime parameters.
According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelism configuration depends either on (1) the parameter
\CodeIn{parallel} to define the parallelism mode within a JVM followed
by the parameter \CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).
Large projects may contain several test suites distributed on
different Maven modules with different configurations. In this case,
we collect the Maven output from each module and we consider only the
distinct configurations. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.
From the \numMedLong{} projects, we identified \numProjectsPar{}
projects with the parallel execution modes \ForkSeq{}, \ParClassSeqMeth{} and
\ParClassParMeth{} enabled by default.
Figure~\ref{tab:freqmodes-dynamic} summarizes our findings. The column
``Group'' indicates the test cost group (see
Figure~\ref{fig:rq1-barplot}), the column ``Subject'' indicates the
name of the project, the column ``\# of modules'' indicates the number
of modules with tests in the default execution, and the column
``Mode'' indicates the corresponding parallelization mode.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}
\begin{figure}[ht!]
    \centering
    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{llcl}
        \toprule
        Group & Subject & \# of modules & Mode\\%
        \midrule%
        Long   & JenkinsCI Gerrit Trigger Plugin & 1 & \ForkSeq{}\\%
        Medium & Apache Logging Log4J2 & 25 & \ForkSeq{}\\%
        Medium & Apache Flink & 74 & \ForkSeq{} \\%
        Medium & BounceStorage Chaos HTTP Proxy & 1 & \ParClassSeqMeth{}\\%
        Medium & Hazelcast Jet & 7 & \ForkSeq{}\\%
        Medium & Jankotek MapDB & 1 & \ParClassParMeth{}\\%
        Medium & Javaslang & 3 & \ParClassParMeth{}\\%
        Medium & Jcabi Github & 1 & \ParClassParMeth{}\\%
        Medium & Spotify Helios & 8 & \ForkSeq{}\\%
        \bottomrule%
    \end{tabular}}
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{figure}

@@

@@

To understand why developers prefer not use parallel test execution,
we considered the \numNonParallel{} subjects that do not use any
parallel mode from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the
\numNonParallel{} projects.
There were \emailsAnswered{} replies from \emailsProjectsAnswered{}, 
and \emailsFalseAnswers{} was not able to explain how the testing works.

@@

\Comment{
\begin{enumerate}
	\item How long does it take for test to run in your
		environment?
	\item Can you briefly define your setup?
	\item Do you confirm that your project does not run in
		parallel?
	\item Select a reason for not using paralellization:
		\begin{enumarate}
			\item I did not know it was possible;
			\item I was concerned with concurrency issues;
			\item I use a continuous integration server;
			\item Some other reason.
		\end{enumerate}
\end{enumerate}
}

From the valid replies, we confirmed that the projects takes more than
\Fix{1m} to run tests and \emailsSeq{} confirmed that those projects do not use 
parallel testing using Maven Surefire. The other projects that we do not 
confirm, need and extra parameter to execute in parallel mode \Luis{make 
sure that they are inside the static analysis sheets made before}.

We noticed that \pctEmailsCI{} of developers use an continuous integration 
server to run tests, \pctEmailsLocal{} run tests in the
development machine, \pctEmailsDidNotSpecify{} did not specified their
testing setup. We also observed that one project has testing enabled 
without parallelization. However the maintainers do not execute the tests.
Considering developers did not know about the existence of the
parallelism configuration \pctEmailsDoNotKnow{} of the replies
confirmed that. Three of the developers also confirmed that they use
another method of parallelization with a distributed build machines.

>>>>

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  We noted
two extreme cases: \CodeIn{JCabi} and \CodeIn{Log4J2}, which most test
classes run one, two, or three test methods with the configuration
\textbf{C2}, without the reutilization of JVM forks. This specific
configuration is useful when there is the need to isolate the test
class execution from another, which is the case.
\Luis{$\leftarrow$ rework this} \Fix{falar
  sobre o resultado geral dos speedups - elaborar menor e maior
  speedup... acho que so vale a pena discutir quando tiver conviccao
  dos 2 casos}

@@

Research questions \numRQC{} and \numRQE{} investigate to which extent
parallelization is used in practice.  It is important to investigate
adoption as it is possible that developers may use alternative
mechanisms to execute tests.

\begin{itemize}
    \item \numRQC. \emph{\RQC}
\end{itemize}

To answer \numRQC{}, we selected all projects that ran in at least one
minute, \ie, projects from the \medg{} and \longg{} groups.  This set
includes \numMedLong{} projects (see Section~\ref{sec:rqA}).  We
looked for dynamic and static manifestations of parallelism.
Section~\ref{sec:rqC-1} and~\ref{sec:rqC-2} report results for each of
these cases.

\vspace{1ex}
\subsubsection{Test execution with parallelism enabled by default}
\label{sec:rqC-1}

To find dynamic evidence of parallelism, we ran the test suites from
our set of \numMedLong{} projects to output all key-value pairs of
Maven parameters.  To that end, we used the option~\CodeIn{-X} to
produce debug output and the option~\CodeIn{-DskipTests} to skip
execution of tests.  We observed that only bootstrapping execution
suffices to discover which parallel configuration modes Maven will
actually use.  According to Maven's
documentation~\cite{maven-surefire-plugin}, any parallelism
configuration depends either on (1) the parameter \CodeIn{parallel} to
define the parallelism mode within a JVM followed by the parameter
\CodeIn{threadCount} or (2) the parameter
\CodeIn{forkCount}\footnote{This parameter is named \CodeIn{forkMode}
  in old versions of Maven Surefire} to define the number of forked
JVMs. For each execution, we capture theses parameters and their
values to map to one of the possible parallelization modes.  For
instance, if a given project contains a module with the parameter
\CodeIn{<forkCount>1C</forkCount>}, the possible classifications are
\ForkSeq{} or \ForkParMeth{} depending on the presence and the value
of the parameter \CodeIn{parallel} (\ie, the presence of
\CodeIn{<parallel>methods</parallel>} results in the parallel mode
\ForkParMeth{}).  Large projects may contain several test suites
distributed on different Maven modules with different
configurations. In this case, we collect the Maven output from each
module discarding duplicates. For instance, if a project contains two
modules with the same parallelism mode, we count only one occurrence
to not inflate our results.

%% Column
%% ``Group'' indicates the test cost group (see
%% Figure~\ref{fig:rq1-barplot}), the

%\begin{figure}[t!]
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \footnotesize
    \centering
    \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8 & \ForkSeq{}\\%
        Javaslang & 3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
%    }
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
    %\end{figure}
\end{wrapfigure}      
Figure~\ref{tab:freqmodes-dynamic} shows the projects we idendified
where parallelism is enabled by default.  Column ``\emph{Subject}''
indicates the name of the project, column ``\emph{\# of modules}''
indicates the number of detected modules containing tests, and column
``\emph{Mode}'' shows the parallel configuration mode used in those
modules (see Section~\ref{sec:modes}).  It came as a surprise the
observation that no project used distinct configurations in their
modules.\Mar{$\leftarrow$ table indicates this.  please confirm.}
Considering our set of \numMedLong{} projects, we found that only
\textbf{\numProjectsPar{}} of those projects had parallelism enabled
by default, with only configurations \ParClassSeqMeth{},
\ParClassParMeth{}, and \ForkSeq{} being used.  Configurations
\ParClassParMeth{} and \ForkSeq{} were the most popular among these
cases.  Note that these results under-approximate real usage of
parallelism as we used default parameters in our scripts to spawn the
Maven process.  That decision could prevent execution of particular
test modules.  To complement this experiemnt, we also looked in
\emph{pom.xml} files for the presence of parallelism.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-dynamic.pdf}
%    \caption{\label{fig:freqmodes-dynamic}\Fix{fix
%    caption}Distribution of parallel modes identified dynamically in a
%    subset of \numProjectsPar{} projects.  A project may have support
%    to more than one parallel mode. Also, a project may run only a
%    subset tests in parallel by default.}
%\end{figure}

@@

\Mar{----------------------- estou aqui}

@@

To understand why developers prefer not use parallel test execution,
we considered \numNonParallel{} subjects that do not use parallel
configuration as default test execution from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the 
\numNonParallel{} projects, and we did not found any e-mail from
\Fix{??} projects using \CodeIn{git} tool.
\Luis{Here I want to say that I could not found any valid e-mail using
\textit{git log}}
There were \emailsAnswered{} replies from \emailsProjectsAnswered{}
projects, and \emailsFalseAnswers{} developers was not able to 
explain how the testing works or was not able to answer the survey.

@@

%% \begin{enumerate}
%% 	\item How long does it take for test to run in your
%%		environment?
%%	\item Can you briefly define your setup?
%%	\item Do you confirm that your project does not run in
%%		parallel?
%%	\item Select a reason for not using paralellization:
%%		\begin{enumarate}
%%			\item I did not know it was possible;
%%			\item I was concerned with concurrency issues;
%%			\item I use a continuous integration server;
%%			\item Some other reason.
%%		\end{enumerate}
%% \end{enumerate}

Based on the answers from the developers, we confirmed that most of
the subjects execution time was compatible with the results found at
Section~\ref{sec:rqA}. From Question I, we noticed that \emailsCI{}
developers confirmed the use of an continuous integration server to
run tests, which \emailsDistributed{} of them is using a distributed
continuous integration server as an alternative to parallelism.
From a local development, \emailsLocal{} developers answered that they
run tests in a local machine, and \emailsNotDescribed{} developers did
not described their environment.
From Question II, we noticed that \emailsSequential{} confirmed that
they do not execute tests in parallel, and \emailsParallel{} did not
confirmed, however, the developers confirmed the need of an extra
parameter at the command line to execute in parallel.
From Question III, \emailsA{} of developers do not know that
parallelism is an available configuration for Maven Surefire,
\emailsB{} of developers do not use parallel testing concerned with
concurrency issues, \emailsD{} of developers uses a continuous
integretion server for run tests while working \Luis{here I want to
say that they use it for something like "non-blocking testing" while
developing in a local machine}, \emailsD{} of developers thinks that
it is not worthy the effort, and \emailsNA{} of developers did not
answered the last question, or did not knew an answer.

\Luis{Pie chart}
